Packaging research artifacts with RO-Crate

### 2021-05-17 latex/ro-crate.tex
Sync

% Two or more authors:
\author[A,B]{\fnms{Stian} \snm{Soiland-Reyes}\ead[label=e1]{soiland-reyes@manchester.ac.uk}\ead[label=o1,orcid]{0000-0001-9842-9718}%
\thanks{Corresponding author. \printead{e1}.}},
\author[C]{\inits{P.S.}\fnms{Peter} \snm{Sefton}\ead[label=e2]{Peter.Sefton@uts.edu.au}\ead[label=o2,orcid]{0000-0002-3545-944X}},
\author[I]{\inits{M.C.}\fnms{Mercè} \snm{Crosas}\ead[label=e9]{mcrosas@g.harvard.edu}\ead[label=o9,orcid]{0000-0003-1304-1939}},
\author[G]{\inits{M.LR.}\fnms{Marco} \snm{La Rosa}\ead[label=e7]{m@lr.id.au}\ead[label=o7,orcid]{0000-}},
\author[E]{\inits{S.L.}\fnms{Simone} \snm{Leo}\ead[label=e5]{simone.leo@crs4.it}\ead[label=o5,orcid]{0000-0001-8271-5429}},
\author[F]{\inits{M.P.}\fnms{Marc} \snm{Portier}\ead[label=e6]{marc.portier@vliz.be}\ead[label=o6,orcid]{0000-0002-9648-6484}},
\author[H]{\inits{D.G.}\fnms{Daniel} \snm{Garijo}\ead[label=e8]{dgarijo@fi.upm.es}\ead[label=o8,orcid]{0000-0003-0454-7145}},
\author[I]{\inits{A.T.}\fnms{Ana} \snm{Trisovic}\ead[label=e9]{ana.trisovic@gmail.com}\ead[label=o9,orcid]{0000-0003-1991-0533}},

\author[D]{RO-Crate Community},
\author[B]{\inits{P.G.}\fnms{Paul} 
\snm{Groth}\ead[label=e3]{p.t.groth@uva.nl}\ead[label=o3,orcid]{0000-0003-0183-6910}}
\author[A]{\inits{C.G.}\fnms{Carole} \snm{Goble}\ead[label=e3]{carole.goble@manchester.ac.uk}\ead[label=o3,orcid]{0000-0003-1219-2137}},
\address[A]{Computer Science, \orgname{The University of Manchester},
\cny{UK}\printead[presep={\\}]{e1,o1}}
\address[B]{Informatics Institute, \orgname{University of Amsterdam},
\cny{The Netherlands}\printead[presep={\\}]{e2,o2}}
\address[C]{Faculty of Science, \orgname{University Technology Sydney},
\cny{Australia}\printead[presep={\\}]{e3,o3}}
\address[E]{\orgname{Center for Advanced Studies, Research, and Development in Sardinia} (CRS4), Pula (CA), \cny{Italy}\printead[presep={\\}]{e5,o5}}
\address[D]{\url{https://www.researchobject.org/ro-crate/community} (see appendix B)}

\address[H]{Ontology Engineering Group, \orgname{Universidad Politécnica de Madrid},
Madrid, \cny{Spain}\printead[presep={\\}]{e8,o8}}

\address[I]{Institute for Quantitative Social Science, \orgname{Harvard University} Cambridge, MA,  \cny{USA}\printead[presep={\\}]{e9,o9}}

>>>>

% Two or more authors:
\author[A,B]{\fnms{Stian} \snm{Soiland-Reyes}\ead[label=e1]{soiland-reyes@manchester.ac.uk}\ead[label=o1,orcid]{0000-0001-9842-9718}%
\thanks{Corresponding author. \printead{e1}.}},
\author[C]{\inits{P.S.}\fnms{Peter} \snm{Sefton}\ead[label=e2]{Peter.Sefton@uts.edu.au}\ead[label=o2,orcid]{0000-0002-3545-944X}},
\author[I]{\inits{M.C.}\fnms{Mercè} \snm{Crosas}\ead[label=e9]{mcrosas@g.harvard.edu}\ead[label=o9,orcid]{0000-0003-1304-1939}},
\author[H]{\inits{D.G.}\fnms{Daniel} \snm{Garijo}\ead[label=e8]{dgarijo@fi.upm.es}\ead[label=o8,orcid]{0000-0003-0454-7145}},
\author[G]{\inits{M.LR.}\fnms{Marco} \snm{La Rosa}\ead[label=e7]{m@lr.id.au}\ead[label=o7,orcid]{0000-}},
\author[E]{\inits{S.L.}\fnms{Simone} \snm{Leo}\ead[label=e5]{simone.leo@crs4.it}\ead[label=o5,orcid]{0000-0001-8271-5429}},
\author[F]{\inits{M.P.}\fnms{Marc} \snm{Portier}\ead[label=e6]{marc.portier@vliz.be}\ead[label=o6,orcid]{0000-0002-9648-6484}},
\author[I]{\inits{A.T.}\fnms{Ana} \snm{Trisovic}\ead[label=e9]{ana.trisovic@gmail.com}\ead[label=o9,orcid]{0000-0003-1991-0533}},

\author[D]{RO-Crate Community},
\author[B]{\inits{P.G.}\fnms{Paul} 
\snm{Groth}\ead[label=e3]{p.t.groth@uva.nl}\ead[label=o3,orcid]{0000-0003-0183-6910}},
\author[A]{\inits{C.G.}\fnms{Carole} \snm{Goble}\ead[label=e3]{carole.goble@manchester.ac.uk}\ead[label=o3,orcid]{0000-0003-1219-2137}}

\address[A]{Computer Science, \orgname{The University of Manchester},
\cny{UK}\printead[presep={\\}]{e1,o1}}
\address[B]{Informatics Institute, \orgname{University of Amsterdam},
\cny{The Netherlands}\printead[presep={\\}]{e2,o2}}
\address[C]{Faculty of Science, \orgname{University Technology Sydney},
\cny{Australia}\printead[presep={\\}]{e3,o3}}
\address[E]{\orgname{Center for Advanced Studies, Research, and Development in Sardinia} (CRS4), Pula (CA), \cny{Italy}\printead[presep={\\}]{e5,o5}}
\address[D]{\url{https://www.researchobject.org/ro-crate/community} (see appendix B)}
\address[H]{Ontology Engineering Group, \orgname{Universidad Politécnica de Madrid},
Madrid, \cny{Spain}\printead[presep={\\}]{e8,o8}}
\address[I]{Institute for Quantitative Social Science, \orgname{Harvard University} Cambridge, MA,  \cny{USA}\printead[presep={\\}]{e9,o9}}

%% TODO: Fix this mess - it seems we need one \address per author
%% as this address also print their individual email and orcid,
%% meaning some organization will repeat.
